\documentclass[../main.tex]{subfiles}
\begin{document}

\chapter{Regions and Branch Cuts}
\section{Terminology}
    \subsection{Neighborhood}
        A \textbf{neighborhood} of a point is a disk of some nonzero radius centered at that point.
    
    \subsection{Open}
        A region is said to be \textbf{open} if it doesn't contain its boundary.
        Every point in the region has a neighborhood also contained in the region.
    
    \subsection{Closed}
        Closed regions are not a major topic in this class as it focuses majorly on topology.
    
    \subsection{Connected}
        A region is said to be \textbf{connected} if you can get from any one point in the region to another point in the region without leaving the region.
        There is a curve contained in the region from initial to final.


    \subsection{Domain}
        A region is said to be a \textbf{domain} if it is open and connected.

    \subsection{Simply Connected}
        A connected region is said to be \textbf{simply connected} if its boundary is connected (only works for complex analysis - not 3D).
        In a more general topological sense, every closed loop in a simply connected region can be deformed to a point in that region without leaving the region. (no holes).

\section{Modifying Regions and Branch Cuts}
    Consider $|z|>0$. This by itself is a non-simply connected domain. But, suppose points along a ray from the origin to the point at infinity is deleted from the domain.
    This simply connects the domain. This cut is called a branch cut.

\section{Branch Points}
    Consider $f(z)=\sqrt{z^{2}-1}$. Notice that the negative real axis is a branch cut. 
    However, suppose we manipulated the function $f(z)=\sqrt{z^{2}-1}=i\sqrt{1-z^{2}}$. This now has 2 branch cuts on the real axis.
    \subsection{Main Idea}
        Algebraic manipulation can change branch cuts but branch points always stay the same. Branch points are where endpoints of the branch cuts.
        Not only that, algebraic manipulation can change the function itself!

    \subsection{Technical Definition}
        Can't be defined properly 

\end{document}
